Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
macro and typo fix

The results are in Table~\ref{table:weights}, where ``Name'' is the
name of the attack and ``base'' is the result of
\tname\ with all heuristic functions enabled, as in ``Rank
(step 3)'' in Table~\ref{table:results}. The remaining columns are the
results when suppressing one heuristic
function. The number corresponds to the order of hte heuristic function
as introduced on Section~\ref{sec:ranking}. The up arrow
($\uparrow$) indicates that the performance is worse when compared to ``base'',
whereas, a down arrow ($\downarrow$), 
highlighted in the table, indicates the contrary.

@@

\noindent\textbf{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in corresponding papers. Unfortunately, side comparison was not
possible for two central reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results was not realistic. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that.

>>>>

The results are in Table~\ref{table:weights}, where ``Name'' is the
name of the attack and ``base'' is the result of
\tname\ with all heuristic functions enabled, as in ``Rank
(step 3)'' in Table~\ref{table:results}. The remaining columns are the
results when suppressing one heuristic
function. The number corresponds to the order of the heuristic function
as introduced on Section~\ref{sec:ranking}. The up arrow
($\uparrow$) indicates that the performance is worse when compared to ``base'',
whereas, a down arrow ($\downarrow$), 
highlighted in the table, indicates the contrary.

@@

\noindent\textbf{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in corresponding papers. Unfortunately, side comparison was not
possible for two central reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results was not realistic. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname\ captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that.
